peters_elements_causal_inference

### 2021-04-24 references/peters_Causality.Rmd
xyz

>>>>

Importance of noise and additional complexity due to causal nature. 
This is called causal learning.

SCM using equations in terms of assignment rather than mathematical equations.
SCM entails a joint distribution over all observables.

# Time

Time often necessary but not modelled specifically or well defined. 
Usually relationship envolved dynamical process but it is not always well defined.
Typically hard sciences involve more concise measures of time than social sciences.

# Relationship mechanical models

SCM somewhere betweren mechanisitic model with differential equations and statistical model

## Chapter 2
